Helixer: Cross-species Gene Annotation Of Large Eucaryotic Genomes Using Deep Learning

### 2020-04-29 paper/main.tex
some files moved, minor

\section{Discussion}
We propose a gene calling model that is able to perform cross-species genomic annotiation for a wide variety of large eucaryotic genomes. Our model does this while outperforming AUGUSTUS on a base pair wise level and withstanding RNASeq data based scrutiny.

>>>>

\section{Discussion}
We propose a novel way to develop gene calling models that are able to perform cross-species genomic annotiation for a wide variety of large eucaryotic genomes. Helixer does this while outperforming AUGUSTUS on a base pair wise level and withstanding RNASeq data based scrutiny.
